---
title: "Lab 10"
author: "Yumeng Gao"
date: "`r Sys.Date()`"
output: 
 github_document:
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos= c(CRAN= "https://cran.rstudio.com"))
```

## Data Setup
```{r}
# install.packages(c("RSQLite", "DBI"))
if(!require(RSQsite)) install.packages("RSQLite")
if(!require(DBI)) install.packages("DBI")

library(RSQLite)
library(DBI)
```

```{r}
# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
actor <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/actor.csv")
rental <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/rental.csv")
customer <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/customer.csv")
payment <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/payment_p2007_01.csv")

# Copy data.frames to database
dbWriteTable(con, "actor", actor)
dbWriteTable(con, "rental", rental)
dbWriteTable(con, "customer", customer)
dbWriteTable(con, "payment", payment)

dbListTables(con)
```

* sql commands (similar to str() in r)
```{sql, connection=con, output.var= "x1"}
PRAGMA table_info(actor)
```

```{r}
x1
```

* do sql from r
```{r}
dbGetQuery(con,"
           PRAGMA table_info(actor)
           "
)
```


# Exercise 1
Retrive the actor ID, first name and last name for all actors using the actor table. Sort by last name and then by first name.
```{sql, connection=con}
SELECT actor_id, first_name, last_name
FROM actor
ORDER by last_name, first_name
LIMIT 15
```

```{r}
dbGetQuery(con,"
SELECT actor_id, first_name, last_name
FROM actor
ORDER by last_name, first_name
LIMIT 15
")
```


# Exercise 2
Retrive the actor ID, first name, and last name for actors whose last name equals ‘WILLIAMS’ or ‘DAVIS’.
```{r}
dbGetQuery(con,"
SELECT actor_id, first_name, last_name
FROM actor 
WHERE last_name IN ('WILLIAMS', 'DAVIS')
ORDER BY last_name
")
```


# Exercise 3
Write a query against the rental table that returns the IDs of the customers who rented a film on July 5, 2005 (use the rental.rental_date column, and you can use the date() function to ignore the time component). Include a single row for each distinct customer ID.

```{r}
dbGetQuery(con,"
           PRAGMA table_info(rental)
           "
)
```

```{r}
dbGetQuery(con,"
SELECT DISTINCT customer_id, rental_date
FROM rental
WHERE date(rental_date) = '2005-07-05'
")
```


```{r}
dbGetQuery(con,"
SELECT DISTINCT customer_id,
COUNT (*) AS N
FROM rental
WHERE date(rental_date) = '2005-07-05'
GROUP BY customer_id
")
```

#Exercise 4

## Exercise 4.1
Construct a query that retrives all rows from the payment table where the amount is either 1.99, 7.99, 9.99.
```{r}

```

## Exercise 4.2
Construct a query that retrives all rows from the payment table where the amount is greater then 5



## Exercise 4.3
Construct a query that retrives all rows from the payment table where the amount is greater then 5 and less then 8


# Exercise 5
Retrive all the payment IDs and their amount from the customers whose last name is ‘DAVIS’.


# Exercise 6

##Exercise 6.1
Use COUNT(*) to count the number of rows in rental





Run the following chunk to disconnect from the connection.
```{r}
# clean up
dbDisconnect(con)
```



















