---
title: "Lab 04"
author: "Yumeng Gao"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r}
library(webshot)
webshot::install_phantomjs()
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Read in the data
First download and then read in with data.table:fread()
```{r}
library(R.utils)
library(data.table)
library(tidyverse)
library(lubridate)
```


```{r read-data, cache= TRUE}
if (!file.exists("met_all.gz"))
  download.file(
    url = "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
    destfile = "met_all.gz",
    method   = "libcurl",
    timeout  = 60
    )
met <- data.table::fread("met_all.gz")
```



## 2. Prepare the data
```{r}
# Remove temperatures less than -17C
# Make sure there are no missing data in the key variables coded as 9999, 999, etc
met <- met[temp>-17] [elev == 9999.0, elev := NA]

# check no 9999s in other important variables
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)
```

Generate a date variable using the functions as.Date() (hint: You will need the following to create a date paste(year, month, day, sep = "-")).
```{r create-ymd,, cache= TRUE }
met= met[ , ymd := as.Date(paste(year, month, day, sep = "-"))]
```

Using the data.table::week function, keep the observations of the first week of the month.
```{r}
met[, table(week(ymd))]
met= met[week(ymd)==31]
```

Compute the mean by station of the variables temp, rh, wind.sp, vis.dist, dew.point, lat, lon, and elev.
```{r check max}
met[, .(
  temp= max(temp, na.rm=T),
  rh= max(rh, na.rm=T),
  wind.sp= max(wind.sp, na.rm=T),
  vis.dist= max(vis.dist, na.rm=T), 
  dew.point= max(dew.point, na.rm=T), 
  lat= max(lat, na.rm=T), 
  lon= max(lon, na.rm=T), 
  elev= max(elev, na.rm=T)
)]
```
```{r check-avg}
met_avg= met[, .(
  temp= mean(temp, na.rm=T),
  rh= mean(rh, na.rm=T),
  wind.sp= mean(wind.sp, na.rm=T),
  vis.dist= mean(vis.dist, na.rm=T), 
  dew.point= mean(dew.point, na.rm=T), 
  lat= mean(lat, na.rm=T), 
  lon= mean(lon, na.rm=T), 
  elev= mean(elev, na.rm=T)
), by= 'USAFID']
```

Create a region variable for NW, SW, NE, SE based on lon = -98.00 and lat = 39.71 degrees
```{r}
met_avg= met_avg[ , region := fifelse(lon>= -98 & lat> 39.71, "NE",
                 fifelse(lon< -98 & lat> 39.71, "NW",
                 fifelse(lon< -98 & lat<= 39.71, "SW","SE")))
     ]
table(met_avg$region)
```

Create a categorical variable for elevation as in the lecture slides
```{r}
met_avg[, elev_cat := fifelse(elev >252, "high", "low")]
```

## 3. Use geom_violin to examine the wind speed and dew point temperature by region
```{r violin-dewpoint}
met_avg[!is.na(region)] %>% 
  ggplot() + 
  geom_violin(mapping = aes(x = 1, y = dew.point, color=region, fill= region)) + 
  facet_wrap(~ region, nrow = 1)
```
the highest dew point temp is in se

```{r violin-wind.sp}
met_avg[!is.na(region) & !is.na(wind.sp)] %>% 
  ggplot() + 
  geom_violin(mapping = aes(x = 1, y = wind.sp, color=region, fill= region)) + 
  facet_wrap(~ region, nrow = 2)
```
ne has the highest wind speed

## 4. Use geom_point with stat_smooth to examine the association between dew point temperature and wind speed by region
Colour points by region
Make sure to deal with NA category
Fit a linear regression line by region
Describe what you observe in the graph
```{r scatterplot-dewpoint-wind.sp}
met_avg[!is.na(region) & !is.na(wind.sp)] %>% 
  ggplot(mapping = aes(x = wind.sp, y = dew.point)) + 
  geom_point(mapping= aes(color= region)) + 
  geom_smooth(method= lm, mapping= aes(linetype= region))+
  facet_wrap(~ region, nrow = 2)
```


```{r}

```



## 5. Use geom_bar to create barplots of the weather stations by elevation category coloured by region
```{r}

```


## 6. Use stat_summary to examine mean dew point and wind speed by region with standard deviation error bars
```{r}

```



## 7. Make a map showing the spatial trend in relative h in the US
```{r}

```


## 8. Use a ggplot extension

```{r}

```

