---
title: "Lab 05"
author: "Yumeng Gao"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r}
library(webshot)
webshot::install_phantomjs()
```


## 1. Read in the data
First download and then read in with data.table:fread()
```{r}
library(R.utils)
library(data.table)
library(tidyverse)
library(lubridate)
library(dtplyr)
```


```{r read-data, cache= TRUE}
if (!file.exists("../lab03/met_all.gz"))
  download.file(
    url = "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
    destfile = "met_all.gz",
    method   = "libcurl",
    timeout  = 60
    )
met <- data.table::fread("../lab03/met_all.gz")
```

```{r}
# Remove temperatures less than -17C
# Make sure there are no missing data in the key variables coded as 9999, 999, etc
met <- met[temp>-17] [elev == 9999.0, elev := NA]
```

## 2. Load the met data
```{r}
# Download the data
stations <- fread("ftp://ftp.ncdc.noaa.gov/pub/data/noaa/isd-history.csv")
stations[, USAF := as.integer(USAF)]

# Dealing with NAs and 999999
stations[, USAF   := fifelse(USAF == 999999, NA_integer_, USAF)]
stations[, CTRY   := fifelse(CTRY == "", NA_character_, CTRY)]
stations[, STATE  := fifelse(STATE == "", NA_character_, STATE)]

# Selecting the three relevant columns, and keeping unique records
stations <- unique(stations[, list(USAF, CTRY, STATE)])

# Dropping NAs
stations <- stations[!is.na(USAF)]

# Removing duplicates
stations[, n := 1:.N, by = .(USAF)]
stations <- stations[n == 1,][, n := NULL]
```

## 3.Merge met data with stations
```{r}
met= merge(
  x = met,
  y = stations,
  by.x = "USAFID",
  by.y = "USAF",
  all.x = TRUE,
  all.y = FALSE
)
```

## Question 1: Representative station for the US.

Computer mean temperature, wind speed and atmospheric pressure for each weather station, and pick the weather stations with the average value closet to the median for the US.
```{r}
station_averages =
  met[, .(
    temp= mean(temp, na.rm=T),
    wind.sp= mean(wind.sp, na.rm=T),
    atm.press= mean(atm.press, na.rm=T)
  ), by= USAFID]
```

The above computes the mean by weather station.
Now let's compute the median value for each variable.
```{r}
statmedians= station_averages[, .(
  temp50 = median(temp, na.rm=T),
  windsp50 = median(wind.sp, na.rm=T),
  atmpress50 = median(atm.press, na.rm=T)
)]
statmedians
```


```{r}
summary(station_averages[ , temp])
```

A helpful function: 'which.min()'.
```{r}
station_averages[ , 
                  temp_dist50 := abs(temp- statmedians$temp50)][order(temp_dist50)]
```

```{r}
station_averages[ which.min(temp_dist50)]
```
It matches the result above.

## Question 2: Representative station per state.

Just like the previous question, you are asked to identify what is the most representative, the median, station per state. This time, instead of looking at one variable at a time, look at the euclidean distance. If multiple stations show in the median, select the one located at the lowest latitude.

```{r}
station_averages =
  met[, .(
    temp= mean(temp, na.rm=T),
    wind.sp= mean(wind.sp, na.rm=T),
    atm.press= mean(atm.press, na.rm=T)
  ), by=  .(USAFID, STATE)]
```

```{r}
statemeds= station_averages[, .(
  temp50 = median(temp, na.rm=T),
  windsp50 = median(wind.sp, na.rm=T),
  atmpress50 = median(atm.press, na.rm=T)
),by= STATE]
statemeds
```

```{r}
station_averages= 
  merge(
  x= station_averages,
  y= statemeds,
  by.x= "STATE",
  by.y= "STATE",
  all.x= T,
  ALL.y= F
)
```



```{r}
station_averages[ , temp_dist_state50 := temp- temp50]
station_averages[ , windsp_dist_state50 := wind.sp- windsp50]             
station_averages[ , atmpress_dist_state50 := atm.press- atmpress50]      
```

```{r}
station_averages[ , eucdist := temp_dist_state50^2 +
                    windsp_dist_state50^2]
station_averages[ , .(
  rep50= min(eucdist))
  , by=STATE]
```

```{r}
repstation= station_averages[ , .(
  eucdist= min(eucdist))
  , by=STATE]
```

```{r}
test= merge(
  x= station_averages,
  y= repstation,
  by.x= c("eucdist","STATE"),
  by.y= c("eucdist","STATE"),
  all.x= F,
  all.y= T
)
```












