---
title: "Lab 03"
author: "Yumeng Gao"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Read in the data
First download and then read in with data.table:fread()

```{r}
library(R.utils)
library(data.table)
library(tidyverse)

if (!file.exists("met_all.gz")){
  download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz", "met_all.gz", method="libcurl", timeout = 60)
}

met <- data.table::fread("met_all.gz")
```

## 2. Check the dimensions, headers, footers. How many columns, rows are there?

```{r}
dim(met)
head(met)
tail(met)
```

## 3. Take a look at the variables.
```{r}
str(met)
```

## 4. Take a closer look at the key variables.
```{r}
table(met$year)
```

```{r}
table(met$day)
```

```{r}
table(met$hour)
```

```{r}
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)
```
OR
```{r}
met[,summary(temp)]
```

Replace elevations with 9999 as NA.
```{r}
met[met$elev==9999.0] <- NA
summary(met$elev)
```


The weather station with highest elevation is at `r max(met$elev,na.rm=TRUE)` meters.


Remove temp below -40 Celsius.

```{r}
met <- met[temp>-40]
met2 <- met[order(temp)]
head(met2)
```

## 5. Check the data against an external data source.

```{r}
met <- met[temp>-15]
met2 <- met[order(temp)]
head(met2)
```


## 6. Calculate summary statistics

```{r}
elev <- met[elev==max(elev)]
summary(elev)
```


```{r}
met[elev==max(elev,na.rm=T), summary(wind.sp)]
```

```{r}
met[elev==max(elev,na.rm=T), .(
  temp_wind= cor(temp, wind.sp, use= "complete"),
  temp_hour= cor(temp, hour, use= "complete"),
  wind.sp_day= cor(wind.sp, day, use= "complete"),
  wind.sp_hour= cor(wind.sp, hour, use= "complete")
)]
```


## 7. Exploratory graphs
```{r}
hist(met$elev, breaks=100)
```
```{r}
hist(met$temp)
```
```{r}
hist(met$wind.sp)
```
```{r}
if (!require(leaflet)){
  install.packages("leaflet")
}
library(leaflet)
leaflet(elev) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)
```


```{r}

```



