---
title: "lab07"
author: "Yumeng Gao"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R.utils)
library(lubridate)
library(tidyverse)
library(tidytext)
library(dplyr)
library(dtplyr)
library(data.table)
library(tidyr)
library(ggplot2)
library(forcats)

library(stringr)
library(rvest)
library(xml2)
library(httr)
```

## Question 1: How many sars-cov-2 papers?
Build an automatic counter of sars-cov-2 papers using PubMed. 
```{r}
# Downloading the website
website <- xml2::read_html("https://pubmed.ncbi.nlm.nih.gov/?term=sars-cov-2")

# Finding the counts
counts <- xml2::xml_find_first(website, "/html/body/main/div[9]/div[2]/div[2]/div[1]/div[1]/span")

# Turning it into text
counts <- as.character(counts)

# Extracting the data using regex
stringr::str_extract(counts, "[0-9,]+")
```

## Question 2: Academic publications on COVID19 and Hawaii
You need to query the following The parameters passed to the query are documented here.
Use the function httr::GET() to make the following query:
Baseline URL: https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esearch.fcgi
Query parameters:
  db: pubmed
  term: covid19 hawaii
  retmax: 1000

```{r}
query_ids <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esearch.fcgi",
  query = list(
    db= "pubmed",
    term= "covid19 hawaii",
    retmax= 1000
  ), 
)

# Extracting the content of the response of GET
ids <- httr::content(query_ids)
```

## Question 3: Get details about the articles
The Ids are wrapped around text in the following way: <Id>... id number ...</Id>. we can use a regular expression that extract that information. 
```{r}
# Turn the result into a character vector
ids <- as.character(ids)

# Find all the ids 
ids <- stringr::str_extract_all(ids, "<Id>[[:digit:]]+</Id>")[[1]]

# Remove all the leading and trailing <Id> </Id>. Make use of "|"
ids <- stringr::str_remove_all(ids, "</?Id>")
```


Grab publications with pubmed id 
```{r}
publications <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi",
  query = list(
    db= "pubmed",
    id= paste(ids,collapse = ","),
    retmax= 1000,
    rettype= "abstract"
    )
)

# Turning the output into character vector
publications <- httr::content(publications)
publications_txt <- as.character(publications)
```








